A-maze of Natural Stories: Texts are comprehensible using the Maze task

### 2021-02-04 Papers/Paper/manuscript.Rmd
edits to paper

```{r setup, include = FALSE}
library("papaja")
library("citr")
library(patchwork)
library(here)
library(tidyverse)
library(readr)
library(brms)
library(lme4)
library(rstan)
library(tidybayes)
library(knitr)
library(matrixStats)
library(tidyverse)
library(readr)
library(brms)
library(lme4)
library(rstan)
library(tidybayes)
library(knitr)
library(mgcv)
library(mgcViz)
library(tidymv)
library(rsample)
library(cowplot)
library(scales)
r_refs("r-references.bib")
theme_set(theme_bw())
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
options(knitr.table.format = "pdf")
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```
# Intro
[TODO: hook about toolbox of methods]
A diversity of robust methods provides for converging evidence from different methods (either within or between types), and choices allow for a good fit to the scope and goals of research. But we also want these methods to be reliable. Some of that is theoretical, but we also want empirical evidence that what the method captures is relevant to what we want to study, and that this connection is true across as broad a range of materials as we hope to use it for. Robustness is important to establishing how good a new method is. What range of tasks can this new tool accomplish and how well? (Could really extend on a toolbox analogy.)

[incrementality; so need incremental methods] 
One question in psycholinguistics is how real-time comprehension works; as we read or listen, we process language incrementally, building and changing our mental model of a sentence. How long we spend on each word is due to both qualities of the word itself and how it fits with the sentence context so far TODO citations

We process language incrementally, building a model of the sentence as we hear or read word.  When a word is unexpected and does not fit the model of the sentence so far, our understanding of the sentence may need to be revised. Incremental processing methods measure this process, tracking how long each word takes to read as a proxy for how hard it is to process and incoroporate into the mental conception of meaning. Fluent language uses process language rapidly and flexibly adapt to many unexpected words. This makes it harder to capture reading time effects because they may be obscured by the overall robust reading process. Different techniques handle this localization problem differently, and present different trade-offs. The two most commonly used methods are eye-tracking and self-paced reading, but neither of these techniques are ideal at localization. One measure of localization is whether current or past word reading time is more predictive. SPR and eye-tarcking both don't seem great.

[eye-track and SPR, failure to localize] TODO: possibly shorten? In eye-tracking, participants read text freely from a screen, while the eye movements and fixations are tracked with an infrared camera CITE, check for truth. Eye-tracking is naturalistic and yields fine-grained data about how long participants spent on each word when, but it's expensive to run requiring both specialized equipment and researcher time to run experiments. Self-paced reading (commonly abbreviated SPR) in contrast can be run online with no specialzed equipment or direct researcher supervision, and so it's possible to collect data quickly and cheaply. In SPR, participants see one word of the text on screen at a time and press a button to contine to the next word instead; the time between button presses when a word was on screen is used as the reading time. The problem with SPR, especially when run online, is that effects from one word tend to show up as longer reading times spread out over several later words, in what is known as spillover effects. Both of these methods suffer somewhat from analytic flexibilty as processing difficulty may manifest in several ways in eye-tracking and is hard to localize in SPR.

[Maze]An alternative that seems to have superior localization is the Maze task, which adopts an unnatural way of reading to force incremental processing. In the Maze task, participants see two words at a time, one of which continues the sentence, and one of which does not, and they have to choose which word is the correct continuation. The time to choose the correct word is taken as the dependent measure and interpreted as representing the difficulty of integrating the word into the sentence so far. If participants make a mistake, the sentence discontinues. Theoretically, participants must fully integrate each word into the sentence in order to confidently select it and move on. This is suppported by studies finding localized effects without much spillover.

[A-Maze] However, traditional Maze materials are effort-instensive to construct, because of the need to select infelicitious words as distractors for each spot of each sentence; this may have kept this method from widespread adoption.

CITE US propose a solution to this problem of generating Maze distractors. In A-maze, distractors are automatically generated by feeding the correct sentences through a program that uses NLP language models to select high-surprisal distractors. The quality of the automatically generated distractors is not up to that of hand-generated distractors, in that the distractors ocassionally are good fits in context. Nonetheless, Boyce et al found that materials with A-maze distractors had similar results to G-maze distractors.  TODO: talk about the paradigm more
[Summary of 2020 paper]

[Summary other uses of A-maze - Slogett]
Slogett also found that it works similarly.

While new and untested, A-maze seems like a potentially powerful addition to the toolkit. However, like the other Maze tasks it has been limited in its application to single-sentence items probing minimal comparisons in constructed sentences. It's only been used on minimal pair types of sentences where each sentence is independent. In particular, it hasn't been used on longer, naturalistic texts, so we don't know how in compares to other methods here. And hasn't been used on multi-sentence issue of generating Maze materials has been proposed. An alternative version of the Maze task, dubbed A-maze, was recently introduced that gets around this problem by automatically generating distrators using a program and neural nets (Boyce et al, 2020). While the quality of the automatically generated distractors is not quite up that of hand-generated (as judged by their being occassional distractors that seem completely acceptable continuations), the results from A-maze match those of G-maze. Boyce et al provide an interface for running the Maze task in a browser and a way of generating distractors that are usually, although not always, sufficiently bad.

In a comparison between these A-maze materials and traditional hand-crafted distractors (from Witzel 2012), they find that A-maze yields comparable results to G-maze (either lab or web), and in one condition recovers effects that G-maze did not. A-maze also outperforms self-paced reading on this syntactic disambiguation paradigm. Sloggett (cite) also directly compared A-maze and G-maze on a disambiguaton paradigm and similarly found that A-maze and G-maze yielded similar results.

These demonstrations make A-maze seem quite promising, as it has the advantages of the traditional Maze task, without it's drawback. This method seems worth exploring further.

[why do longer Maze] While some psycholinguistic phenomena are well-explored within individual targeted sentences, there's also a need for reading time data of more naturalistic passages. This is important as a comparison for models of language understanding, for correlating with NLP language models. In addition, some phenomena such as discourse effects, only work in the context of passages. THus, it would be useful/versatile if Maze could be used in these other contexts.

[short-coming, where's the question we need to answer] One evident shortcoming of the Maze task is that it has been used on only a limited set of materials. Some of this is due to the fact that it isn't used as widely as other incremental processing methods, and some is due to inherent limitations of the paradigm. In particular, because Maze tasks discontinue after participants make mistakes, the farther into an item a word is, the fewer participants see it. This makes it hard to run long materials using Maze, and prevents Maze from being used on long text passages where SPR or eye-tracking could be used.

[Our contribution is...] We find a way around this problem by creating a version of the Maze task interface where participants correct their mistakes and continue with the sentence rather than being discontinued. This allows for multi-sentence items to be run using Maze, which we verify by running Maze on the Natural Stories corpus. With this data, we are able to confirm that participants can comprehend what they read using Maze and investigate the effects of surprisal on RT in Maze.

# Error-correction maze

[review the terminate thing, and why it was there] The advantage of the Maze task is that it forces incremental processing and automatically excludes inattentive participants by terminating a sentence when a participant makes an error. Thus, only participants who have processed the sentence up that point and are paying attention contribute data at critical regions later in the sentence. However, this means we don't have data after a participant makes a mistake in an item. In traditional G-maze tasks, with hand-crafted distractors and attentive participants, this is a small issue as the low per-word error rate does not compound too badly over the individual sentences.

[ how this causes problems for 2020 and theoretically] 
However, this data loss was worse with A-maze materials and crowd-sourced participants [@boyceMazeMadeEasy2020]. The high errors could be from participants guessing randomly or from auto-generated distractors that in fact fit the sentence. @boyceMazeMadeEasy2020 noted that some distractors, especially early in the sentence were problematic and caused considerable data loss.

Given the appeals of using A-maze, it would be adventageous to get around this problem. Additionally, even with attentive participants and good distractors, the Maze paradigm will eventually run into problems as error rates compound over long materials, and few participants will make it to the end. For instance, with a 1% error rate, `r round(.99**15*100)`% would complete each 15-word sentence, but only `r round(.99**50*100)`% of participants would complete each 50 word vignette, and `r round(.99**200*100)`% each 200 word passages.  In order to run longer materials, we need something to do when participants make a mistake, other than terminate the entire item.

To resolve this, we introduce an *error-correction* variant of Maze, where we let participants continue on when they make a mistake. To do this, we present them with an error message, and wait until they select the correct option, before continuing the sentence as normal. We make this "error-correction" Maze available as an option in a modification of the Ibex Maze implementation introduced in CITE ME (TODO repo link). The code records both the RT to the first click and also the total RT until the correct answer is selected as separate values. TODO diagram goes here

[ why this error thing seems really cool and could work] 
Our goal is that this error-correction will minimize the problems of having occassional poor auto-generated distractors by letting participants continue on and still read the whole item. It will also enable us to run long materials on Maze, thus expanding the range of questions that Maze can be used on.

@@

We constructed A-maze distractors for the Natural stories corpus (CITE) and recruited 100 MTurkers to each read a story in the Maze paradigm.

## Materials (good)
We took the texts of the Natural Stories corpus (CITE) and split it into sentences because the A-Maze process works on the sentence level. (This involved some judgment calls due to quoted speech). We used the original comprehension questions provided in the Natural Stories corpus. To familiarize participants with the task, we wrote a short practice passage and corresponding comprehension questions.
We then ran the sentences of the items through the A-maze generation process. We updated the code of the generation process to fix some issues identified in that paper; the code used is available at REPO. The underlying method did not change, but features such as appropriately handling more types of punctuation (needed for the Natural Stories corpus) were added. We ran the materials using FOOBAR paramters. We used the auto-generated distractors as they were, without checking them for quality. Materials are available at REPO.
TODO other notable changes to the codebase??

## Participants
We recruited 100 participants from Amazon Mechanical Turk, and paid each participant 3.50 dollars. We estimated that reading a 1000 word story would take 17 minutes at 1 word/second (based on previous work), so we expected the task to take around 20 minutes total. In fact, it appears to have taken most attentive participants around 20 minutes to read the story, and thus closer to 25 minutes for the overall study. We excluded data from those who did not report English as their native language, leaving `r data_filt %>% select(subject) %>% unique() %>% nrow()` participants.

@@

## Reading stories in the Maze task (good)

(ref:error-cap) A. Correlation between a participant's accuracy on the Maze task (fraction of words selected correctly) and their average reaction time (in ms). Many participants (marked in green) chose the correct word >80% of the time; others (in red) appear to be randomly guessing and were excluded from further analysis. B. Performance on comprehension questions. Participants who had >80% task accuracy tended to do well on comprehension questions; those who were at chance on the task were also at chance on comprehension questions.

```{r errors, out.height="25%", fig.width=6, fig.height=2, fig.pos='t', fig.cap="(ref:error-cap)"}
error_plot <- ggplot(data_error_summ, aes(x=pct_correct, y=mean_rt, color=accurate))+
  geom_point(size=1)+
  labs(x="Fraction words selected correctly",
       y="Mean Reaction Time (ms)")+
  coord_cartesian(xlim=c(0.4,1), ylim=c(0,1600), expand=F)+
    scale_color_manual(values=c(">80% correct"="darkgreen","<80% correct"="darkred"))+
  guides(color=FALSE)

@@

Another check is whether participants comprehended the story. We counted how many of the binary-choice comprehension questions each participant got right (out of 6), and group them by their performance on the Maze task. As seen in @ref(fig:errors)B, most participants were were accurate on the task also did well on comprehension questions, while participants who were at chance on the Maze task were also at chance on the comprehension questions. Participants usually answered quickly (within 10 seconds), so we do not believe they were looking up the answers on the internet. These are not especially hard questions, and we can't rule out that some participants may have been able to guess the answers without reading the story. Nonetheless, this provides preliminary evidence that people can understand and remember details of stories they read during the Maze task.

@@

The relationship between a word's predictability and it's reading time is of interest. CITE It's well-established that for eye-tracking and SPR, RTs are roughly linear in term of a words surprisal (negative log probability). We wanted to check if this linear relationship also holds for Maze. Two other common word-features that affect RT are word length and a word's overall frequency. CITE

To assess this, we create a set of predictors of frequency, word length, and surprisals from several models. For length, we use the length of characters (excluding end punctuation). For a measure of unigram frequency, we tokenize the CITE gulordava training data (this tokenizes off punctuation, but preserves case) and tally up instances. For the models, we use the log2 frequency of the expected occurances in 1 billion words (thus frequency is log, but higher values indicate higher frequency words). For surprisals, we get per-word surprisals for each of 3 different language models: a Kneser-Ney smoothed 5-gram, GRNN CITE, and Transformer-XL CITE. We center, but do not rescale these predictors. For all of these predictors, we consider both the predictor at the current word as well as lagged predictors from the previous word. CITE some SPR stuff This is an additional test of localization. The model formula we use is rt ~ surp* length +  freq * length + past_surp * past_length + past_freq * past_length.

@@

### GAM
For GAM models, we center length and frequency but not surprisal. We want surprisal interpretable, but we also will be plotting it (at least for the bootstrapping) at length and frequencies set to 0, so they need to be centered. (Not sure this last piece is actually true/matters).

## Try 1
Using only pre-error data.

Does not have hierarchical effects. Has smooths for the surprisals, and tensor effects/interactions for the freq x length

```{r}
#mean by subject for each word
labelled_pre_error <- read_rds(paste0(here(),"/Analysis/pre_error.rds"))
d_lm <- labelled_pre_error %>% group_by(word, txl_center, ngram_center, grnn_center, freq_center, length_center,
                                        past_c_txl, past_c_ngram, past_c_grnn, past_c_freq, past_c_length, Word_ID) %>% 
  summarize(mean_rt=mean(rt))
```

```{r for gam}

@@

all_data <- ngram_data %>% union(grnn_data) %>% union(txl_data) %>% 
  select(surprisal, prev_surp,model) %>% 
  pivot_longer(cols=`surprisal`:`prev_surp`) %>% 
  mutate(s=ifelse(name=="surprisal", "Current","Previous"))
```

```{r gams, eval=F}
gam_ngram_1 <- gam(rt ~ s(surprisal, bs="cr", k=20)+ te(freq, len, bs="cr")+s(prev_surp, bs="cr", k=20)+te(prev_freq, prev_len, bs="cr"), data=ngram_data, method="REML")

gam_grnn_1 <- gam(rt ~ s(surprisal, bs="cr", k=20)+ te(freq, len, bs="cr")+s(prev_surp, bs="cr", k=20)+te(prev_freq, prev_len, bs="cr"), data=grnn_data, method="REML")

gam_txl_1 <- gam(rt ~ s(surprisal, bs="cr", k=20)+ te(freq, len, bs="cr")+s(prev_surp, bs="cr", k=20)+te(prev_freq, prev_len, bs="cr"), data=txl_data, method="REML")

@@

```{r plot-gam, eval=F}

a <- get_gam_predictions(model=gam_ngram_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="5-gram", s="Current")
b <- get_gam_predictions(model=gam_ngram_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="5-gram", s="Previous")
c <- get_gam_predictions(model=gam_grnn_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GRNN", s="Current")
d <- get_gam_predictions(model=gam_grnn_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GRNN", s="Previous")
e <- get_gam_predictions(model=gam_txl_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="TXL", s="Current")
f <- get_gam_predictions(model=gam_txl_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="TXL", s="Previous")
```

```{r, eval=F}
all <- a %>% union(b) %>% union(c) %>% union(d) %>% union(e) %>% union(f)

gam1 <-  ggplot(all, aes(x=surprisal, y=rt, ymin=CI_lower, ymax=CI_upper))+
  geom_line()+
  geom_ribbon(alpha=.3)+
   #geom_density(data=all_data, aes(x=value), fill="gray",)+
  facet_grid(s~model)+
  coord_cartesian(ylim=c(700,1300), xlim=c(0,28))+
  labs(x="Surprisal (bits)", y="Reaction Time (ms)")+theme(axis.ticks.x=element_blank(), axis.title.x=element_blank(), axis.text.x=element_blank(), plot.margin=margin(t=0,r=0,b=0,l=0,unit="pt"))

dens2 <-   ggplot(all_data, aes(x=value))+
  geom_density(fill="gray",)+
  facet_grid(.~model)+
  labs(x="Surprisal (bits)", y="")+
  theme(axis.text.y = element_blank(), strip.text=element_blank(), axis.ticks.y =element_blank(), axis.title.y=element_blank(), panel.grid=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "cm"))

bot <- plot_grid(NA, dens2, NA, nrow=1, rel_widths = c(.16, 1, .08))

 plot_grid(gam1, bot, nrow=2, rel_heights = c(1, .3))

#confirm that this really is just a prettied up version of what the usual output is
#plot(gam_txl_1, seWithMean = TRUE, shift = coef(gam_txl_1)[1], select=1)

@@

### Frequentist LMs

## Models

@@

@@

## What if we don't exclude participants

One potentially useful comparison with past SPR/eye-tracking is if we are more inclusive of participants, do we get data that looks more like theirs. (Perhaps our exclusion criteria are more robust?)

This is all data from participants who speak English that wasn't a mistake. (So, includes bad participants and post-mistake data.)

```{r freq_all}
#mean by subject for each word
labelled_anything_goes <- read_rds(paste0(here(),"/Analysis/non-selective.rds"))
d_lm2 <- labelled_anything_goes %>% group_by(word, txl_center, ngram_center, grnn_center, freq_center, length_center,
                                        past_c_txl, past_c_ngram, past_c_grnn, past_c_freq, past_c_length, Word_ID) %>% 
  summarize(mean_rt=mean(rt))
```

no_surp <- lmer(mean_rt ~ freq_center*length_center+past_c_freq*past_c_length+(1|word), data=d_lm2)

ngram_only <- lmer(mean_rt ~ ngram_center + past_c_ngram + freq_center*length_center+past_c_freq*past_c_length+(1|word), data=d_lm2)

grnn_only <- lmer(mean_rt ~ grnn_center + past_c_grnn + freq_center*length_center+past_c_freq*past_c_length+(1|word), data=d_lm2)

txl_only <- lmer(mean_rt ~ txl_center + past_c_txl + freq_center*length_center+past_c_freq*past_c_length+(1|word), data=d_lm2)

#summary(no_surp)
#summary(ngram_only)
#summary(grnn_only)
#summary(txl_only)

BRM models from this same very permissive data. 
```{r brm-models}

any_grnn <- read_rds(paste0(here(),"/Analysis/brm_grnn_any_center.rds"))
any_txl <- read_rds(paste0(here(),"/Analysis/brm_txl_any_center.rds"))
any_ngram <- read_rds(paste0(here(),"/Analysis/brm_ngram_any_center.rds"))

#summary(any_grnn)
#summary(any_txl)
#summary(any_ngram)

>>>>

```{r setup, include = FALSE}
 library("papaja")
 library("citr")
 library(here)
 library(tidyverse)
library(patchwork)
 library(brms)
 library(lme4)
 library(tidybayes)
 library(mgcv)
 library(cowplot)
 library(gridExtra)
r_refs("r-references.bib", append=F)
theme_set(theme_bw())
options(knitr.table.format = "pdf")
```
# Intro
We process language incrementally, building a model of the sentence as we hear or read word.  When a word is unexpected and does not fit the model of the sentence so far, our understanding of the sentence may need to be revised. Incremental processing methods measure how long each word takes to read as a proxy for how hard it is to incoroporate into the mental model of the sentence. Fluent language uses process language rapidly and flexibly adapt to many unexpected words, which makes it hard to pinpoint slow downs related to difficult-to-process words.

TODO motivate why we care about localization

The two most commonly used methods are eye-tracking and self-paced reading. Both these methods are known to have spillover effects, which makes localization harder. CITE some things TODO might be worth bringing up RT/surprisal/spillover findings hereOur next question is what the relationship between a word's predictability and it's reading time is for Maze. It's well established for eye-tracking and SPR that RTs are roughly linear in terms of a word's surprisal (negative log probability). Due to spillover effects, on SPR and eye-tracking, there is also a positive linear relationship between the surprisal of a previous word and the RT on the current word -- this is an indication of lack of localization. In addition to suprisal predicting RT, word length and word's overall frequency are also often found to be predictive. TODO many CITES

An alternative method that seems to have superior localization is the Maze task, which adopts an unnatural way of reading to force incremental processing [@forsterMazeTaskMeasuring2009]. In the Maze task, participants see two words at a time, a correct word that continues the sentence, and a distractor which does not. Participants must choose the correct word, and their reaction time (RT) is the dependent measure. If participants make a mistake, the sentence discontinues. Theoretically, participants must fully integrate each word into the sentence in order to confidently select it. This idea is supported by studies finding strongly localized effects [@witzel12].

The downside of Maze is that materials are effort-intensive to construct because of the need to select infelicitious words as distractors for each spot of each sentence; this may explain why the Maze task was not widely adopted. 
@boyceMazeMadeEasy2020 demonstrate a way to automatically generate Maze distractors by using NLP language models to find words that are high-surprisal in the context of the target sentence. The quality of these A-Maze distractors is not up to that of hand-generated distractors, but @boyceMazeMadeEasy2020 found that materials with A-maze distractors had similar results to the hand-generated distractors from @witzel12. @sloggettAmazeAnyOther also found that A-maze and G-maze distractors yielded similar results on a disambiguation paradigm.

While new, A-maze seems like a potentially powerful addition to the psycholinguists toolkit. However, like the other Maze tasks it has been limited in its application to single-sentence items probing minimal comparisons in constructed sentences. While some psycholinguistic phenomena are well-explored within individual targeted sentences, there's also a need for reading time data on longer passages, for instance in order to compare to language models or study discourse effects. Therefore, it's important to test whether the Maze task works on these types of materials.

While the issue of needing to generate distractors for long passages is solved with A-maze, another problem with Maze remains. In particular, because Maze tasks discontinue after participants make mistakes, the farther into an item a word is, the fewer participants see it. This makes it hard to run long materials using Maze, and prevents Maze from being used on long text passages where SPR or eye-tracking could be used.

We address this problem by creating a Maze task interface where participants correct their mistakes and continue with the sentence rather than terminating on mistakes. This allows for multi-sentence items to be run using Maze, which we verify by running Maze on the Natural Stories corpus. With this data, we are able to confirm that participants can comprehend what they read using Maze and investigate the effects of surprisal on RT in Maze.

# Error-correction maze
(ref:diagram-cap) Schematic of error-correction Maze. A participant reads a sentence word by word, choosing the correct word at each time point (selections marked in blue). When they make a mistake, an error message is displayed, they try again, and continue with the sentence.

```{r diagram, out.height="25%", fig.width=8, fig.height=3, fig.pos='t', fig.cap="(ref:diagram-cap)"}
knitr::include_graphics(paste0(here(),"/Papers/maze_diagram_cropped.pdf"))
```
One advantage of the Maze task is that it forces incremental processing and automatically excludes inattentive participants by terminating a sentence when a participant makes an error. Thus, only participants who have processed the sentence and are paying attention contribute data at critical regions later in the sentence. However, this means we don't have data after a participant makes a mistake in an item. In traditional G-maze tasks, with hand-crafted distractors and attentive participants, this is a small issue. However, this data loss is much worse with A-maze materials and crowd-sourced participants [@boyceMazeMadeEasy2020]. The high errors are likely from some combination of participants guessing randomly and from auto-generated distractors that in fact fit the sentence; as @boyceMazeMadeEasy2020 noted, some distractors, especially early in the sentence, were problematic and caused considerable data loss.

We could try to improve the situation by auto-generating better distractors or hand-replacing problematic ones. However, the inherent data losses poses a more fundamental problem: even with attentive participants and good distractors, the Maze paradigm will eventually run into problems as error rates compound over long materials where few participants will make it to the end. For instance, with a 1% error rate, `r round(.99**15*100)`% would complete each 15-word sentence, but only `r round(.99**50*100)`% of participants would complete a 50 word vignette, and `r round(.99**200*100)`% a 200 word passages.  In order to run longer materials, we need something to do when participants make a mistake, other than terminate the entire item.

To resolve this, we introduce an *error-correction* variant of Maze, where we let participants continue on when they make a mistake. We present them with an error message and wait until they select the correct option, before continuing the sentence as normal. This *error-correction* variant is shown in Figure \@ref(fig:diagram). We make this "error-correction" Maze available as an option in a modification of the Ibex Maze implementation introduced in @boyceMazeMadeEasy2020 (TODO repo link). The code records both the RT to the first click and also the total RT until the correct answer is selected as separate values.

Our goal is that this error-correction will minimize the problems of having occasional poor auto-generated distractors by letting participants continue on and still read the whole item. It will also enable us to run long materials on Maze, thus expanding the range of questions that Maze can be used on.

@@

We constructed A-maze distractors for the Natural stories corpus [@futrellNaturalStoriesCorpus2020] and recruited 100 MTurkers to each read a story in the Maze paradigm.

## Materials
We took the texts of the Natural Stories corpus [@futrellNaturalStoriesCorpus2020] and split it into sentences because the A-Maze process works on the sentence level. We used the original comprehension questions provided in the Natural Stories corpus. To familiarize participants with the task, we wrote a short practice passage and corresponding comprehension questions.
We then ran the sentences of the items through the A-maze generation process. We updated the code of the generation process to fix some issues identified in that paper; the code used is available at REPO. The underlying method did not change, but features such as appropriately handling more types of punctuation (needed for the Natural Stories corpus) were added. We ran the materials using FOOBAR parameters. We used the auto-generated distractors as they were, without checking them for quality. Materials are available at REPO.
TODO other notable changes to the codebase??

## Participants
We recruited 100 participants from Amazon Mechanical Turk, and paid each participant 3.50 dollars. We excluded data from those who did not report English as their native language, leaving `r data_filt %>% select(subject) %>% unique() %>% nrow()` participants.

@@

## Reading stories in the Maze task

(ref:error-cap) A. Correlation between a participant's accuracy on the Maze task (fraction of words selected correctly) and their average reaction time (in ms). Many participants (marked in green) chose the correct word >80% of the time; others (in red) appear to be randomly guessing and were excluded from further analysis. B. Performance on the comprehension questions. Participants who had >80% task accuracy tended to do well on comprehension questions; those who were at chance on the task were also at chance on comprehension questions.

```{r errors, out.height="25%", fig.width=8, fig.height=3, fig.pos='t', fig.cap="(ref:error-cap)"}
error_plot <- ggplot(data_error_summ, aes(x=pct_correct, y=mean_rt, color=accurate))+
  geom_point(size=1)+
  labs(x="Fraction words selected correctly",
       y="Mean Reaction Time (ms)")+
  coord_cartesian(xlim=c(0.4,1), ylim=c(0,1600), expand=F)+
    scale_color_manual(values=c(">80% correct"="darkgreen","<80% correct"="darkred"))+
  guides(color=FALSE)

@@

Another check is whether participants comprehended the story. We counted how many of the binary-choice comprehension questions each participant got right (out of 6), and group them by their performance on the Maze task. As seen in Figure \@ref(fig:errors)B, most participants were were accurate on the task also did well on comprehension questions, while participants who were at chance on the Maze task were also at chance on the comprehension questions. Participants usually answered quickly (within 10 seconds), so we do not believe they were looking up the answers on the internet. These are not especially hard questions, and we can't rule out that some participants may have been able to guess the answers without reading the story. Nonetheless, this provides preliminary evidence that people can understand and remember details of stories they read during the Maze task.

@@

We wanted to see if Maze also showed a linear relationship between surprisal and RT, and whether this was localized at the current word or whether previous word surprisals were also influential. To do this, we created a set of predictors of frequency, word length, and surprisals from several different langauge models, and fit generalized additive models to check for a linear relationship.
 For length, we use the length of characters (excluding end punctuation). For a measure of unigram frequency, we tokenize the training data from @gulordava18 (this tokenizes off punctuation, but preserves case) and tally up instances. For the models, we use the log2 frequency of the expected occurances in 1 billion words (thus frequency is log, but higher values indicate higher frequency words). For surprisals, we get per-word surprisals for each of 3 different language models: a Kneser-Ney smoothed 5-gram, GRNN [@gulordava], and Transformer-XL [@daiTransformerXLAttentiveLanguage2019a]. We centered but did not rescale the length and frequency predictors; for interpretability, we kept surprisal uncentered. For all of these predictors, we consider both the predictor at the current word as well as lagged predictors from the previous word. CITE some papers that did the same thing . We used smooths for the surprisal terms and tensor effects for the frequency by length effects and interactions.

@@

(ref:gam-cap) GAM predictions of reaction time (RT) as a function of either current word surprisal (top) or previous word surprisal (bottom). Density of data is shown along the x-axis. For each of the 3 language models used, there is a linear relationship between current word surprisal and RT (at least when there is enough data). There is no relationship between previous word surprisal and RT.

```{r gam, out.height="40%", fig.width=8, fig.height=3, fig.pos='t', fig.cap="(ref:gam-cap)"}
labelled_pre_error <- read_rds(paste0(here(),"/Analysis/pre_error.rds"))

@@

all_data <- ngram_data %>% union(grnn_data) %>% union(txl_data) %>% 
  select(surprisal, prev_surp,model) %>% 
  pivot_longer(cols=`surprisal`:`prev_surp`) %>% 
  mutate(s=ifelse(name=="surprisal", "Current","Previous"))

all <-read_rds(paste0(here(),"/Analysis/gam_predictions.rds"))
gam1 <-  ggplot(all, aes(x=surprisal, y=rt, ymin=CI_lower, ymax=CI_upper))+
  geom_line()+
  geom_ribbon(alpha=.3)+
   #geom_density(data=all_data, aes(x=value), fill="gray",)+
  facet_grid(s~model)+
  coord_cartesian(ylim=c(700,1300), xlim=c(0,28))+
  labs(x="Surprisal (bits)", y="Reaction Time (ms)")+theme(axis.ticks.x=element_blank(), axis.title.x=element_blank(), axis.text.x=element_blank(), plot.margin=margin(t=0,r=0,b=0,l=0,unit="pt"))

dens2 <-   ggplot(all_data, aes(x=value))+
  geom_density(fill="gray",)+
  facet_grid(.~model)+
  labs(x="Surprisal (bits)", y="")+
  theme(strip.text.x=element_blank(),axis.text.y=element_blank(), panel.grid=element_blank(), axis.ticks.y=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "cm"))

p2 = align_plots(gam1, dens2, align = "v", axis="lr")
plot_grid(p2[[1]], p2[[2]], nrow=2, rel_heights = c(1, .3))

@@

The smooths for the current and previous words surprisals are shown in Figure \@ref(fig:gam). Note that for each of the models, high-surprisal words at relatively rare, with much of the data for words between 0 and 15 bits of surprisal. All of the models show a roughly linear relationship between current word surprisal and RT, especially in the region with more data. All of the models show a flat relationship between previous word surprisal and RT. This is a sign of localization as the previous word's surprisal is not affecting RT, only the word's own suprisal is. The linear relationship matches that found with other methodologies.

Given the linear relationship, we next fit linear models to look at coefficients and model fit. We fit BRMS models.

### BRM models

  stats <- gather_draws(model, `b_.*`, regex=T) %>% 
    mutate(above_0=ifelse(.value>0, 1,0)) %>% 
    group_by(.variable) %>% 
    summarize(pct_above_0=mean(above_0)) %>% 
    mutate(`P` = signif(2*pmin(pct_above_0,1-pct_above_0), digits=2)) %>% 
    left_join(intervals, by=".variable") %>% 
    mutate(lower=round(.lower, digits=1),
           upper=round(.upper, digits=1),
           E=round(.value, digits=1),
           `Estimate`=str_c(E," [",lower,", ", upper,"]"),
           Term=str_sub(.variable, 3, -1),
           ) %>% 
    select(Term, `Estimate`)

```{r pre-error}
brm_txl_interact <- read_rds(paste0(here(),"/Analysis/brm_txl_interact.rds"))
brm_grnn_interact <- read_rds(paste0(here(),"/Analysis/brm_grnn_interact.rds"))
brm_ngram_interact <- read_rds(paste0(here(),"/Analysis/brm_ngram_interact.rds"))
a <- show_summary(brm_txl_interact) %>% mutate(model="TXL") %>% mutate(Term=str_replace(Term,"txl","surp"))
b <- show_summary(brm_grnn_interact) %>% mutate(model="GRNN") %>% mutate(Term=str_replace(Term,"grnn","surp"))
c <- show_summary(brm_ngram_interact) %>% mutate(model="5-gram") %>% mutate(Term=str_replace(Term,"ngram","surp"))

summ <- a %>% union(b) %>% union(c) %>% pivot_wider(names_from="model", values_from=c(`Estimate`)) %>% 
  mutate(Term=factor(Term, 
                        levels=c("Intercept", 
                                 "surp_center",
                                 "length_center",
                                 "freq_center",
                                 "surp_center:length_center",
                                 "length_center:freq_center",
                                 "past_c_surp",
                                 "past_c_length",
                                 "past_c_freq",
                                 "past_c_surp:past_c_length",
                                 "past_c_length:past_c_freq")
                                 )) %>% 
  arrange(Term) %>% 
  mutate(Term=c("Intercept", "Surprisal", "Length", "Frequency",
                  "Surp x Length", "Freq x Length", "Past Surprisal",
                  "Past Length", "Past Freq", "Past Surp x Length", "Past Freq x Length")) %>% 
  select(Term, `5-gram`, `GRNN`, TXL)

knitr::kable(summ, format="latex", position="t",caption="TODO")
```

```{r post-error}
brm_txl_interact_post <- read_rds(paste0(here(),"/Analysis/brm_txl_interact_post.rds"))
brm_grnn_interact_post <- read_rds(paste0(here(),"/Analysis/brm_grnn_interact_post.rds"))
brm_ngram_interact_post <- read_rds(paste0(here(),"/Analysis/brm_ngram_interact_post.rds"))

d <- show_summary(brm_txl_interact_post) %>% mutate(model="TXL") %>% mutate(Term=str_replace(Term,"txl","surp"))
e <- show_summary(brm_grnn_interact_post) %>% mutate(model="GRNN") %>% mutate(Term=str_replace(Term,"grnn","surp"))
f <- show_summary(brm_ngram_interact_post) %>% mutate(model="5-gram") %>% mutate(Term=str_replace(Term,"ngram","surp"))

summ <- d %>% union(e) %>% union(f) %>% pivot_wider(names_from="model", values_from=c(`Estimate`)) %>% 
   mutate(Term=factor(Term, 
                        levels=c("Intercept", 
                                 "surp_center",
                                 "length_center",
                                 "freq_center",
                                 "surp_center:length_center",
                                 "length_center:freq_center",
                                 "past_c_surp",
                                 "past_c_length",
                                 "past_c_freq",
                                 "past_c_surp:past_c_length",
                                 "past_c_length:past_c_freq")
                                 )) %>% 
  arrange(Term) %>% 
  mutate(Term=c("Intercept", "Surprisal", "Length", "Frequency",
                  "Surp x Length", "Freq x Length", "Past Surprisal",
                  "Past Length", "Past Freq", "Past Surp x Length", "Past Freq x Length")) %>% 
  select(Term, `5-gram`, `GRNN`, TXL)

knitr::kable(summ, format="latex", position="t",caption="TODO")

@@

As we can see in Table \@ref(tab:pre-error) and Table \@ref(tab:post-error).

### Model comparison

@@

```{r}
d_lm <- labelled_pre_error %>% group_by(word, txl_center, ngram_center, grnn_center, freq_center, length_center,
                                        past_c_txl, past_c_ngram, past_c_grnn, past_c_freq, past_c_length, Word_ID) %>% 
  summarize(mean_rt=mean(rt))

@@
